---
title: "ASSIGNMENT-integer programming"
author: "rachana"
date: "2022-11-20"
output: pdf_document
---
```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```
library("lpSolveAPI")
```{r}
AP_HUB = read.lp("C:/Users/kurra/Downloads/ap_hub.lp")
AP_HUB
```
*an estimate of the number of workers needed each day of the week has given in the below table.*
```{r}
workers_day_wise = matrix(c("sunday","monday","tuesday","wednesday","thursday","friday","saturday", 18,27,22,26,25,21,19), ncol=2, byrow=F)

colnames(workers_day_wise) = c("Day_of_the_week", "Workers_Required")
workers_day_wise
as.table(workers_day_wise)
```
*Package handlers at AP are guaranteed a five-day work week with two consecutive days off. The base wage for the handlers is $750 per week. Workers working on Saturday or Sunday receive an additional $25 per day. The possible shifts and salaries for package handlers are:*


```{r}
Day_offs_and_wages = matrix(c(1,2,3,4,5,6,7,
                               "Sunday and Monday","Monday and Tuesday","Tuesday and Wednesday","Wednesday and Thursday","Thursday and Friday","Friday and Saturday","Saturday and Sunday",
                               "$775","$800","$800","$800","$800","$775","$750"),ncol=3,byrow=F)

colnames(Day_offs_and_wages)= c("shifts","day_offs","wages")
Day_offs_and_wages

```
```{r}
solve(AP_HUB)
get.objective(AP_HUB)
```
```{r}
get.variables(AP_HUB)
```
*from the variables we can evaluate that no. of workers assigned to particular day as:*


*X1= no. of workers assigned on shift 1=2*
*X2= no. of workers assigned on shift 2=4*
*X3= no. of workers assigned on shift 3=5*
*X4= no. of workers assigned on shift 4=0*
*X5= no. of workers assigned on shift 5=8*
*X6= no. of workers assigned on shift 6=1*
*X7= no. of workers assigned on shift 7=13*

*from the variables we can observe that how many vworkers are available to work each day with respect to the objective function as well as the constraints framed by the organization*

*Sunday = x2 + x3 + x4 + x5 + x6 = 18 Workers*

*Monday = x3 + x4 + x5 + x6 + x7 = 27 Workers*

*Tuesday = x4 + x5 + x6 + x7 + x1 = 24 Workers*

*Wednesday = x5 + x6 + x7 + x1 + x2 = 28 Workers*

*Thursday = x6 + x7 + x1 + x2 + x3 = 25 Workers*

*Friday = x7 + x1 + x2 + x3 + x4 = 24 Workers*

*Saturday = x1 + x2 + x3 + x4 + x5 = 19 Workers*


